\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-10-21 fully-abstract-comp/popl2019/paper.tex
Rewrite seal introduction

In other words, the authority the underlying capability represents is encapsulated.

@@

The right make sealed capabilities is represented by a sets of seals $\seal{\sigma_\var{base},\sigma_\var{end},\sigma}$.

@@

We represent seals in sets rather than single seals to have a more compact representation of multiple seals and make it possible to have seal allocation (not described here).

@@

When capabilities are unsealed with \texttt{xjmp} control will be transferred to a capability that was previously sealed which allows the capability-sealer to decide how the sealed capability is used.

>>>>

In other words, the authority the underlying capability represents is encapsulated under the seal.

@@

The right to make sealed capabilities is represented by a sets of seals $\seal{\sigma_\var{base},\sigma_\var{end},\sigma}$.

@@

On \trgcm{}, we represent seals in sets rather than single seals to have a more compact representation of multiple seals and make it possible to have seal allocation (not described here).

@@

When underlying capabilities are unsealed with \texttt{xjmp}, control will be transferred to one of the underlying capability which allows the capability-sealer to decide how the sealed capabilities are used.
